Software Architectures for Integrating Workflow Engines in Science Gateways

### 2016-05-13 paper.tex
One fix following @najmahan's comments

The pool architecture is overall the most scalable, which is not
surprising since it is designed precisely for scalability. Tight
integration is the least scalable and all the other architectures
perform the same overall. The global scalability score, however,
should not conceal \closednote{Naj}{what do you mean by
  mask?}{Tristan}{I guess 'hide' or 'conceal' are better
  words. Fixed.} the unique characteristics of architectures regarding
this criterion. Nested workflows are the only architecture that can
easily accommodate distributed workflow execution, which can be
critical in some cases. At the same time, the scheduling constraints
created by task encapsulation and nested workflows may become problematic \closednote{Naj}{please don't use these from-film-marketing
  words?! :-) }{Tristan}{OK!} depending on the type of targeted
infrastructure. Non-reliable infrastructures \closednote{Naj}{you mean by
  the showstoppers, i.e. the nested workflows which can accommodate
  distributed executions but are limited by scheduling constraints?}{Tristan}{Yes. I rephrased a bit this part.} ,
for example, could hardly cope with workflow engines being wrapped in
computing tasks as done in task encapsulation. The availability of
multiple engine instances could also become a critical feature for
science gateways with important workloads, which would favor task
encapsulation and pool. \note{Naj}{I feel this paragraph is a bit
  vague, and doesn't distill and contextualize the thorough work
  described before.}

>>>>

The pool architecture is overall the most scalable, which is not
surprising since it is designed precisely for scalability. Tight
integration is the least scalable and all the other architectures
perform the same overall. The global scalability score, however,
should not conceal \closednote{Naj}{what do you mean by
  mask?}{Tristan}{I guess 'hide' or 'conceal' are better
  words. Fixed.} the unique characteristics of architectures regarding
this criterion. Nested workflows are the only architecture that can
easily accommodate distributed workflow execution, which can be
critical in some cases. At the same time, the scheduling constraints
created by task encapsulation and nested workflows may become problematic \closednote{Naj}{please don't use these from-film-marketing
  words?! :-) }{Tristan}{OK!} depending on the type of targeted
infrastructure. Non-reliable infrastructures\closednote{Naj}{you mean by
  the showstoppers, i.e. the nested workflows which can accommodate
  distributed executions but are limited by scheduling constraints?}{Tristan}{Yes. I rephrased a bit this part.},
for example, could hardly cope with workflow engines being wrapped in
computing tasks as done in task encapsulation. The availability of
multiple engine instances could also become a critical feature for
science gateways with important workloads, which would favor task
encapsulation and pool. \note{Naj}{I feel this paragraph is a bit
  vague, and doesn't distill and contextualize the thorough work
  described before.}
